---
title: "Assignment"
author: "Shruti Palamadai"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1: Manipulation
1. Load the dataset EurostatCrime2017.csv. Notice that the first column of the csv file
contains the names of the countries that must be read as row names.

```{r}
EuroCrime  <- read.csv(file="EurostatCrime2017.csv", row.names=1,header=TRUE, sep=",")
#printing sample data:
EuroCrime[5,1:3]
```

2.What is the size (number of rows and columns) and the structure of this dataset?

```{r}
dim(EuroCrime)
```
Thus this dataset has 41 rows and 11 columns (excluding country)

3. Produce appropriate commands to answer the following questions:
(i) For some countries Theft includes also burglary, and theft of motorised land vehicle,
in others they are recorded separately. Add a new column called All Theft which
contains the sum of all the crimes that have a theft component:
 Theft,
 Theft of a motorized land vehicle,
 Burglary,
 Burglary of private residential premises
Please consider NA values as 0 in this case.

```{r}
All_Theft_Data = EuroCrime[,c('Theft','Theft_of_a_motorized_land_vehicle','Burglary','Burglary_of_private_residential_premises')]
EuroCrime$All_Theft <- rowSums(All_Theft_Data,na.rm=TRUE)
EuroCrime$All_Theft
```

(ii) Remove the columns: Theft, Theft of a motorized land vehicle, Burglary, and
Burglary of private residential premises.

```{r}
drop_columns <- c('Theft','Theft_of_a_motorized_land_vehicle','Burglary','Burglary_of_private_residential_premises')
data<-EuroCrime[ , !(names(EuroCrime) %in% drop_columns)]
colnames(data)
```

4. Work with the dataset you created in question 3ii, and list the countries that contain any
missing data.
```{r}
missing_countries = unique(unlist(lapply(data,function(data)which(is.na(data)))))
names=row.names(data)
names[missing_countries]
```
5. Remove the countries with missing data from the dataframe.

```{r}
EuroCrime_new <- data[complete.cases(data),]
```

6. How many observations and variables are in this new dataframe?
```{r}
dim(EuroCrime_new)
```
This new dataframe has 25 rows and 8 columns(excluding country rowname)


## Task 2 : Analysis

Work with the dataset produced in question 6. Produce appropriate commands to answer the
following questions:
1. According to these data what were the 3 most common crimes in Ireland in 2017?

```{r}
Ireland_crimes = subset(EuroCrime_new,row.names(EuroCrime_new) == "Ireland")
colnames(sort(Ireland_crimes[,-1], decreasing = TRUE)[1:3])
```
2. Which country has the highest overall record of offences (per hundred thousand inhabi-
tants)?

```{r}
EuroCrime_new$All_Offences <- rowSums(EuroCrime_new[,-1])
country_with_most_offense <- EuroCrime_new[order(-EuroCrime_new$All_Offences),][1,]
row.names(country_with_most_offense)
```

## Task 3: Creativity
Do something interesting with these data! Create a table or a plot which shows something we
have not discovered above already and outline your findings.

```{r}
library("ggpubr")
ggscatter(EuroCrime_new,x="Kidnapping",y="Sexual.violence",
          add ="reg.line",conf.int=TRUE,
          cor.coef = TRUE, cor.method= "pearson")
```

In the graph we can see that there seems to be a significant correlation between kidnapping and sexual violence.
This is confirmed by calculating the person coefficient and seeing that p-value is less than 0.05 in this case.
Thus we could say that in most cases if there is a kidnapping there is a good chance it may also lead to sexual violence
